\huge Microbial Interaction Database pipeline - Figures draft \#2

### 2018-12-19 figures.tex
Update figure2

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figure2.pdf}
  \caption{
    \textbf{Comparison of representative sequences generated by the various denoising and clustering algorithms used in the workflow.}
    \textbf{(A)} The average weighted UniFrac distance between the representative sequences,
    \textbf{(B)} The average unweighted UniFrac distance,
    \textbf{(C)} The distributions of the average unweighted UniFrac distance between original sequence profile and calculated profile in mock datasets (this will be replaced with a violoin plot)
  }
  \label{fig:figure2}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figure2.pdf}
  \caption{
    \textbf{Comparison of representative sequences generated by the various denoising and clustering algorithms used in the workflow.}
    \textbf{(A)} The average weighted UniFrac distance between the representative sequences,
    \textbf{(B)} The average unweighted UniFrac distance,
    \textbf{(C)} The distributions of the average unweighted UniFrac distance between original sequence profile and calculated sequence profile in mock datasets (this will be replaced with a violoin plot)
  }
  \label{fig:figure2}
\end{figure}
